Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-12 content/background.tex
addressing comments

\otodo{The definitions that Marianna had were for \emph{complete}
lattices/semilattices. All of the lattices in the context of IFDS/IDE
are/must be complete. I'll just say that here.}
\ftodo{Would it make sense to first the define the notion of a lattice without referring to its completeness?
       This could be followed by defining what it means for a (semi)lattice to be complete, and then we
       could say that all lattices considered in this paper are complete, etc.}
\ftodo{Can we define the symbols $\sqcup$ and $\sqcap$ for join and meet here?}
A \textit{complete lattice} is a partially ordered set $(S,\sqsubseteq)$ in which every subset has a least upper bound and a greatest lower bound.
A \textit{complete meet semilattice} is a partially ordered set in which every subset need only have a greatest lower bound.
The symbols $\bot$ and $\top$ are used to denote the greatest lower bound of $S$ and of the empty set, respectively.
Since all of the (semi)lattices discussed in this paper are required to be complete, we will henceforth leave out the
\textit{complete} qualifier.

@@

\subsubsection{Overview of the IDE Algorithm}\label{sec:ideoverview}
Just as any distributive function from $2^D$ to $2^D$ can be represented with a
representation relation, it is also possible to represent any distributive functions from
$\textsf{Env}(D,L)$
to
$\textsf{Env}(D,L)$
with a \textit{pointwise representation}. A pointwise representation is a bipartite graph
with the same nodes~\footnote{The IDE literature uses the symbol $\Lambda$ for the node that
    is denoted $\mathbf0$ in the IFDS literature.}
and edges as a representation relation, except that each edge is labelled
with a \textit{micro-function}, which is a function from $L$ to $L$. 
\commentout{
The pointwise representation of an environment transformer 
$t : \textsf{Env}(D,L) \to \textsf{Env}(D,L)$
is defined as
\newcommand{\microedge}[3]{#1\xrightarrow{#3}#2}
\begin{align*}
    R_t =& \{ \microedge{\Lambda}{\Lambda}{\lambda l.l} \} \cup
    \{\microedge{\Lambda}{d_j}{\lambda l.t(\Omega)(d_j)} \mid d_j \in D\}\\
    &\cup
    \{\microedge{d_i}{d_j}{\lambda l.t(\Omega[d_i\to l])(d_j)} \mid d_i, d_j \in D\}.
\end{align*}
}
Let $\Omega = \lambda d.\top$ be the environment that maps every element of $D$ to $\top$.
\ftodo{
   What is the relationship between $\Omega$ and $\Delta$?
}
Thanks to distributivity, every environment transformer 
$t : \textsf{Env}(D,L) \to \textsf{Env}(D,L)$
can be decomposed into its effect on $\Omega$ and on a set of environments $\Omega[d_i\to l]$
that map every element except one ($d_i$) to $\top$:
\[
    t(m)(d_j) = \lambda l. t(\Omega)(d_j) \sqcap \bigsqcap_{d_i\in D} \lambda l. t(\Omega[d_i\to l])(d_j).
\]
The functions $\lambda l. \cdots$ in this decomposition are the micro-functions that
appear on the edges of the pointwise representation edges from $\Lambda$ to each $d_j$ and from
each $d_i$ to each $d_j$.%
\footnote{The IDE paper defines a more complicated but equivalent set of micro-functions
that eliminate some duplication of computation.}
The absence of an edge in the pointwise representation from some $d_i$ to some $d_j$ is
equivalent to an edge with micro-function $\lambda l.\top$.

@@

\ftodo{Would it make sense to discuss an example of an IDE problem here?  Perhaps we can do this
  without using much space by referring to an existing figure elsewhere in the paper?}

>>>>

\otodo{The definitions that Marianna had were for \emph{complete}
lattices/semilattices. All of the lattices in the context of IFDS/IDE
are/must be complete. I'll just say that here.}
\ftodo{Would it make sense to first the define the notion of a lattice without referring to its completeness?
       This could be followed by defining what it means for a (semi)lattice to be complete, and then we
       could say that all lattices considered in this paper are complete, etc.}
%\ftodo{Can we define the symbols $\sqcup$ and $\sqcap$ for join and meet here?}
A \textit{complete lattice} is a partially ordered set $(S,\sqsubseteq)$ in which every subset has a least upper bound, called \textit{join} or $\sqcup$, and a greatest lower bound, called \textit{meet} or $\sqcap$.
A \textit{complete meet semilattice} is a partially ordered set in which every subset need only have a greatest lower bound.
The symbols $\bot$ and $\top$ are used to denote the greatest lower bound of $S$ and of the empty set, respectively.
Since all of the (semi)lattices discussed in this paper are required to be complete, we will henceforth leave out the
\textit{complete} qualifier.

@@

\subsubsection{Overview of the IDE Algorithm}\label{sec:ideoverview}
Just as any distributive function from $2^D$ to $2^D$ can be represented with a
representation relation, it is also possible to represent any distributive functions from
$\textsf{Env}(D,L)$
to
$\textsf{Env}(D,L)$
with a \textit{pointwise representation}. A pointwise representation is a bipartite graph
with the same nodes~\footnote{The IDE literature uses the symbol $\Lambda$ for the node that
    is denoted $\mathbf0$ in the IFDS literature.}
and edges as a representation relation, except that each edge is labelled
with a \textit{micro-function}, which is a function from $L$ to $L$. 
\commentout{
The pointwise representation of an environment transformer 
$t : \textsf{Env}(D,L) \to \textsf{Env}(D,L)$
is defined as
\newcommand{\microedge}[3]{#1\xrightarrow{#3}#2}
\begin{align*}
    R_t =& \{ \microedge{\Lambda}{\Lambda}{\lambda l.l} \} \cup
    \{\microedge{\Lambda}{d_j}{\lambda l.t(\Omega)(d_j)} \mid d_j \in D\}\\
    &\cup
    \{\microedge{d_i}{d_j}{\lambda l.t(\Omega[d_i\to l])(d_j)} \mid d_i, d_j \in D\}.
\end{align*}
}
Let $\Omega = \lambda d.\top$ be the environment that maps every element of $D$ to $\top$.
\ftodo{
   What is the relationship between $\Omega$ and $\Delta$?
}
\otodo{What do you mean by $\Delta$?}
Thanks to distributivity, every environment transformer 
$t : \textsf{Env}(D,L) \to \textsf{Env}(D,L)$
can be decomposed into its effect on $\Omega$ and on a set of environments $\Omega[d_i\to l]$
that map every element except one ($d_i$) to $\top$:
\[
    t(m)(d_j) = \lambda l. t(\Omega)(d_j) \sqcap \bigsqcap_{d_i\in D} \lambda l. t(\Omega[d_i\to l])(d_j).
\]
The functions $\lambda l. \cdots$ in this decomposition are the micro-functions that
appear on the edges of the pointwise representation edges from $\Lambda$ to each $d_j$ and from
each $d_i$ to each $d_j$.%
\footnote{The IDE paper defines a more complicated but equivalent set of micro-functions
that eliminate some duplication of computation.}
The absence of an edge in the pointwise representation from some $d_i$ to some $d_j$ is
equivalent to an edge with micro-function $\lambda l.\top$.

@@

\ftodo{Would it make sense to discuss an example of an IDE problem here?  Perhaps we can do this
  without using much space by referring to an existing figure elsewhere in the paper?}
\otodo{I have the todo on the previous page to add text referring to the example in Figure 3.}
